Deeply Virtual Compton Scattering measurement off bound protons

### 2018-11-05 eg6-letters/incoherent/incoherent_prl.tex
final version

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=\sqrt{(q+p)^2}$ assuming the initial proton is at rest) greater than 2 
GeV to avoid the nucleon resonance region.  The $t$, transferred momentum 
squared to the recoil proton, calculated from 4-momentum vectors of incoming 
and outgoing photons, was required to be greater than a minimum allowed value 
at given Q$^2$ and 
W~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically use the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. Then, 
we ensured the exclusivity of the incoherent DVCS events by imposing 
a series of constraints based on the four-momentum conservation 
in the reaction $ep\rightarrow e'p'\gamma$. These kinematical 
variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we see no sizeable effect 
that can be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

>>>>

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
than 2 GeV to avoid the nucleon resonance region.  The $t$, transferred 
momentum squared to the recoil proton, calculated from 4-momentum vectors of 
incoming and outgoing photons, was required to be greater than a minimum 
allowed value at given Q$^2$ and 
W~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically use the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. Then, 
we ensured the exclusivity of the incoherent DVCS events by imposing 
a series of constraints based on the four-momentum conservation 
in the reaction $ep\rightarrow e'p'\gamma$. These kinematical 
variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we see no sizeable effect 
that can be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.
